An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-16 indicators/paper/paper.tex
Copyedits to discussion

Research on data revisions in the context of influenza-like illness has shown
that backfill can significantly alter forecast performance \cite{Brooks:2018,
  Reich:2019}, and that careful training on preliminary data can reduce this
influence \cite{Brooks:2020}. Recent research has shown similar results for
COVID-19 forecasts \cite{Kamarthi:2021}. We also investigate this in our
companion paper on forecasting, where we observe that training and validating
models on finalized data yields overly optimistic estimates of true test-time
performance.

@@

The COVIDcast API provides open access to real-time and geographically-detailed
indicators of COVID activity in the United States that support and enhance
standard public health reporting streams in several ways.

First, several signals in the API closely track COVID activity (over both time
and space); yet they are derived from different data streams (such as surveys,
medical insurance claims, and medical devices), and are therefore not subject to
the same sources of error as public health reporting data. This can be important
both for robustness and situational awareness, allowing decision-makers to
diagnose potential anomalies in standard surveillance streams, and for modeling
tasks such as forecasting and nowcasting. Our companion paper on forecasting
discusses this in more detail.

Second, the API features many other signals that are relevant to understanding
aspects of the pandemic and its effects on the United States population that are
not found in traditional public health streams, such as data on mobility
patterns, Internet search trends, mask wearing, and vaccine hesitancy, to name
just a few. (The latter two are derived from the COVID Trends and Impact Survey;
see our companion paper on this survey for a detailed view of its features and
capabilities.) These signals have already supported pandemic research and
policy-making.

Third, the underlying database tracks all revisions made to the data, allowing
us to query the API to learn ``what was known when'', critical for understanding
the behavior (and potential pitfalls) of real-time surveillance signals. Such
revision data is rarely available in standardized form from other sources.

@@

There are a number of open questions, and challenges that remain. Each signal is
subject to different biases, such as survey sampling and nonresponse biases or
geographic differences in market share for medical claims data. Claims data can
also be subject to biases during major national holidays and other events that
change health-seeking behavior. Characterizing these biases will be important
for future research using these signals. Several data sources are also subject
to extensive revision and backfill, which must be studied and modeled to enable
real-time use of these sources in forecasting and nowcasting systems. The
breadth and unique features of the COVIDcast API will help facilitate this work,
which will be vital to advancing pandemic modeling and preparedness.

>>>>

Research on data revisions in the context of influenza-like illness has shown
that backfill can significantly alter forecast performance \cite{Brooks:2018,
  Reich:2019}, and that careful training on preliminary data can reduce this
influence \cite{Brooks:2020}. Recent research has shown similar results for
COVID-19 forecasts \cite{Kamarthi:2021}. We also examine this in our companion  
paper on forecasting, where we observe that training and validating models on
finalized data yields overly optimistic estimates of true test-time
performance.

@@

The COVIDcast API provides open access to real-time and geographically-detailed
indicators of COVID activity in the United States, which supports and enhances
standard public health reporting streams in several ways.

First, several signals in the API closely track COVID activity (over both time
and space); yet they are derived from different data streams (such as surveys,
medical insurance claims, and medical devices), and are thus not subject to the
same sources of error as public health reporting streams. This can be important  
both for robustness and situational awareness, allowing decision-makers to
diagnose potential anomalies in standard surveillance streams, and for modeling
tasks such as forecasting and nowcasting. Our companion paper on forecasting
discusses this in more detail.

Second, the API features many other signals that are relevant to understanding
aspects of the pandemic and its effects on the United States population that are
not found in traditional public health streams, such as data on mobility
patterns, Internet search trends, mask wearing, and vaccine hesitancy, to name
just a few. (The latter two signals are derived from the COVID Trends and Impact
Survey; our companion paper on this survey gives more a detailed view of its
features and capabilities.) These signals have already supported pandemic
research and  policy-making.

Third, the underlying database tracks all revisions made to the data, allowing
us to query the API to learn ``what was known when'', critical for understanding
the behavior (and potential pitfalls) of real-time surveillance signals. Such
revision data is rarely available in standardized format from other sources.

@@

There are a number of open questions, and challenges that remain. Several
signals are subject to biases, such as survey sampling and nonresponse biases,
or geographic differences in market share for medical claims data. Claims data
can also be subject to biases during major national holidays and other events
that change health-seeking behavior. Characterizing these biases will be
important for future research and operational systems that use these
signals. Several data sources are also subject to extensive revision and
backfill, which must be studied and modeled to enable effective real-time use of
these sources in forecasting and nowcasting systems. The breadth and unique
features of the COVIDcast API will help facilitate this work, which will be
vital to advancing pandemic modeling and preparedness.
